Deciding Bitvector Termination with Program Synthesis

### 2014-06-28 papers/termination/paper.tex
added non-termination formula for sequential loops

\begin{definition}[Non-Termination Formula - Closed Recurrence Set {\bf [CNT]}]
\label{def:deterministic-nonterm-formula}
 \begin{align*}
  \exists N, \mathcal{V}_0 . \forall \mathcal{V}, \mathcal{V}' . & I(\mathcal{V}_0) \wedge N(\mathcal{V}_0) ~ \wedge \\
                                                        & N(\mathcal{V}) \rightarrow G(\mathcal{V}) ~ \wedge \\
							& N(\mathcal{V}) \wedge T(\mathcal{V}, \mathcal{V}') \rightarrow N(\mathcal{V}') 
 \end{align*} 
\end{definition}
\end{framed}
\end{figure*}

@@

Our method is purely semantic. %We extend the notion of recurrence set in order to formulate the 
We formulate the non-termination problem at the loop level.%, rather than transition relation.
In our design, a loop $L=(\mathcal{V},I,G,t)$ is non-terminating iff it has a recurrence set of states.

>>>>

\begin{definition}[Non-Termination Formula - Closed Recurrence Set {\bf [CNT]}]
\label{def:deterministic-nonterm-formula}
 \begin{align*}
  \exists N, \mathcal{V}_0 . \forall \mathcal{V}, \mathcal{V}' . & I(\mathcal{V}_0) \wedge N(\mathcal{V}_0) ~ \wedge \\
                                                        & N(\mathcal{V}) \rightarrow G(\mathcal{V}) ~ \wedge \\
							& N(\mathcal{V}) \wedge T(\mathcal{V}, \mathcal{V}') \rightarrow N(\mathcal{V}') 
 \end{align*} 
\end{definition}

\begin{definition}[Sequential Loops Non-Termination Formula {\bf [SNT]}]
\label{def:multi-termination-formula}
 \begin{align*}
  \exists R, Inv_1,..., Inv_n . \forall \mathcal{V}_0,...,\mathcal{V}_n, \mathcal{V}_1',...,\mathcal{V}_n'.  & P_0(\mathcal{V}_0,\mathcal{V}_1) \rightarrow Inv_1(\mathcal{V}_1) ~  \\
 & \bigwedge_{i=1..n{-}1} (Inv_i(\mathcal{V}_i) \wedge G_i(\mathcal{V}_i) \wedge T_i(\mathcal{V}_i, \mathcal{V}_i') \rightarrow Inv_i(\mathcal{V}_i')) ~  \\  
 & \bigwedge_{i=1..n{-}2} (Inv_i(\mathcal{V}_i) \wedge \lnot G_i(\mathcal{V}_i) \wedge P_{i+1}(\mathcal{V}_i, \mathcal{V}_{i+1}) \rightarrow Inv_{i+1}(\mathcal{V}_{i+1})) ~ \wedge \\
 & Inv_{n-1}(\mathcal{V}_{n-1}) \wedge \lnot G_{n-1}(\mathcal{V}_{n-1}) \wedge P_n(\mathcal{V}_{n-1},\mathcal{V}_n) \wedge N(\mathcal{V}_n)  ~ \wedge \\
                                                        & N(\mathcal{V}_n) \rightarrow G_n(\mathcal{V}_n) ~ \wedge 
							 N(\mathcal{V}_n) \wedge T_n(\mathcal{V}_n, \mathcal{V}_n') \rightarrow N(\mathcal{V}_n') 
 \end{align*}
\end{definition}

\end{framed}
\end{figure*}

@@

Our method is purely semantic. %We extend the notion of recurrence set in order to formulate the 
We formulate the non-termination problem at the loop level.%, rather than transition relation.
In our design, a loop $L=(\mathcal{V},I,G,t)$ is non-terminating iff it has a recurrence set of states.\\

{\bf Sequential loops.}
Discuss {\bf [SNT]}.
